Comparing Machine Learning algorithms for classifying cognitive states from fMRI data

### 2012-11-09 article/article.tex
results

\begin{itemize}
	\item Classifiers performance do not differ significantly between them. (explain)
	\item Classifiers performance differ significantly from 50\%.
\end{itemize}

Moreover, it is observed that the Multivariate case has the best performance between all classifiers (why?). When PCA is used for feature extraction, the performance of Naive Bayes is lower than when other feature selection methods are used (why?).

We can also distinguish the fact that when different structure is used for the fitting data, the performance increases, though not significantly. This is observed in the case of the Naive Bayes classifier. When different structure is used, its performance increases approximately 4\%.

>>>>

\begin{itemize}
	\item Classifiers performance do not differ significantly between them. Except from the case that PCA is used, the difference in performance between the classifiers for the rest of the cases is not more than 10\%.
	\item Classifiers performance differ significantly from 50\%.
\end{itemize}

Moreover, it is observed that the Multivariate case has the best performance between. When PCA is used for feature extraction, the performance of Naive Bayes is lower than when other feature selection methods are used.

We can also distinguish the fact that when different structure is used for the fitting data, the performance increases, though not significantly. For example, in the case of the Naive Bayes classifier when different structure is used, its performance increases approximately 4\%.

Comparing classifiers when the same structure is used, it is observed that Linear SVM performs better than Naive Bayes. The same remains true when comparing the Multivariate case with Naive Bayes. The former one has better performance.
